Mapping factors associated with adolescents' emotion dysregulation: A text-mining based systematic review

### 2020-06-09 manuscript.Rmd
Finished analyses for study 1

The corpus for this first analysis consisted of the author-provided keywords for the selected articles.
We extracted keywords by document, and used a dictionary approach
to classify related terms.
The dictionary was created specifically for this study.
The lead author composed a first draft of the dictionary based on prior knowledge of the field.
This draft was subsequently updated in two ways:
First, while writing the introduction for this paper, key terms from the theoretical and empirical literature were added to the dictionary.
Second, by including commonly occurring uncategorized words during preliminary analyses of the data.
An exclusion list of methodological terms and other non-substantive words was generated using the same procedure.

@@

```{r}
if(run_everything) source("LDA_analysis.R")
```
To assess the homogeneity of the corpus, we conducted topic modeling using latent dirichlet allocation [@bleiLatentDirichletAllocation2003]. 
A range of 2-20 topics was considered.
Fit was evaluated based on the BIC, and interpretability was evaluated on the entropy of the posterior probabilities of documents to be assigned to the different topics.
The BICs followed a near-perfect linearly increasing trend, indicating that no subcorpora could be identified.
Congruently, all entropies were near-zero, which means that the posterior probabilities of documents to be assigned to the different topics were uniformly distributed.
Thus, no interpretable subcorpora could be identified, and we proceed with an analysis of the whole sample. <!-- Probably because each set of keywords has only a few indicators. -->

>>>>

```{r}
source("study1.R")
if(run_everything | !file.exists("Study1_lda_dims.txt")) source("LDA_analysis.R")
lda_dims <- read_yaml("Study1_lda_dims.txt")
```
The corpus for this first analysis consisted of the author-provided keywords for the selected articles.
We extracted keywords by document, and used a dictionary,
created specifically for this study,
to classify related terms.
The dictionary describes `r length(dict)` terms using `r length(unlist(dict))`
regular expression queries.
The lead author composed a first draft of the dictionary based on prior knowledge of the field.
This draft was subsequently updated in two ways:
First, while writing the introduction for this paper, key terms from the theoretical and empirical literature were added to the dictionary.
Second, by including commonly occurring uncategorized words during preliminary analyses of the data.
An exclusion list of methodological terms and other non-substantive words was generated using the same procedure.
After applying the dictionary and exclusion filter,
and removing records with no (remaining) keywords,
the resulting corpus consisted of `r number_docs_words["docs"]` documents with `r number_docs_words["words"]` unique words.
As term-document frequency is irrelevant in the context of keywords (i.e., keywords should not occur twice within the same document, except when two synonyms have been recoded using the dictionary),
the term-document matrix was dichotomized.

@@

To assess the homogeneity of the corpus, we conducted topic modeling using latent dirichlet allocation [@bleiLatentDirichletAllocation2003].
For this analysis, we used the term frequency/inverse document frequency (TF-IDF) to select terms
not used frequently in the corpus,
which could therefore be more diagnostic of subgroup membership.
Selection terms with an TF-IDF greater than the median resulted in a corpus of `r lda_dims[1]` documents and `r lda_dims[2]` terms.
We considered a range from 2-20 topics, evaluating fit based on the BIC, and interpretability based on the entropy of the posterior document/topic probabilities.
The BICs followed a near-perfect linearly increasing trend, indicating that no subcorpora could be identified.
Congruently, all entropies were near-zero, which means that the posterior document/topic probabilities were effectively uniformly distributed.
Thus, no interpretable subcorpora could be identified,
and we proceed with an analysis of the whole sample. <!-- Probably because each set of keywords has only a few indicators. -->

## Mapping the literature

To map the cooccurrence of terms within documents,
it is pertinent to select the most common terms, instead of using IDF.
As a cutoff, we required terms to occur in at least $0.5%$ of documents.
This selection criterion resulted in a corpus of `r dim(dtm_top)[1]` documents and `r dim(dtm_top)[2]` terms.
The marginal occurrence of the selected terms is displayed in Figure \@ref(study1wordcloud).
To determine the frequency with which terms were addressed in documents,
we constructed a term-document matrix

```{r study1wordcloud, fig.cap="Wordcloud of terms selected for Study 1 co-occurrence analysis. More common words are centered and printed in larger font."}
knitr::include_graphics("study1_wordcloud.png")
```

### 2020-06-09 manuscript.tex
Finished analyses for study 1

Papers were screened based on two main criteria: First, papers had to address emotion regulation, emotional problems, or similar. Second, the target population must overlap (at least in part) with adolescence, defined as the age range from 10-25. Thus, for example, an article reviewing the role of hormonal changes in emotional adjustment throughout the entire life course, including adolescence, would be deemed relevant. Screening was initially conducted in Rayyan QRCI ({\textbf{???}}). Papers were sorted using Rayyan's ranking algorithm. To train the algorithm on exclusion criteria, screening focused on abstracts most likely to be excluded. After coding 559 papers, screening continued in ASReview - a free, open source alternative to Rayyan QRCI ({\textbf{???}}). This program uses text mining and active learning to build a customizable machine learning model for article inclusion. We used a naive Bayes model, and focused on exclusion of irrelevant papers. In ASReview, an additional 541 papers were screened. Screening again focused on articles most likely to be excluded, and continued until, among the most recently screened 100 papers, only 6 were excluded. The screening procedure is detailed in Figure \ref{prismachart}. In total, 6305 papers were retained for analysis.

\begin{figure}
\centering
\includegraphics{manuscript_files/figure-latex/prismachart-1.pdf}
\caption{\label{fig:prismachart}Record screening flowchart}
\end{figure}

@@

For this first analysis, we relied on author-provided keywords.
We extracted keywords by document, and used a dictionary approach
to classify closely related terms.

@@

@@

>>>>

Papers were screened based on two main criteria:
First, papers had to address emotion regulation, emotional problems, or similar.
Second, the target population must overlap (at least in part) with adolescence, defined as the age range from 10-25.
Thus, for example, an article reviewing the role of hormonal changes in emotional adjustment throughout the entire life course, including adolescence, would be deemed relevant.
Screening was initially conducted in Rayyan QRCI (Ouzzani, Hammady, Fedorowicz, \& Elmagarmid, 2016).
Papers were sorted using Rayyan's ranking algorithm.
To train the algorithm on exclusion criteria, screening focused on abstracts most likely to be excluded.
After coding 559 papers, screening continued in ASReview - a free, open source alternative to Rayyan QRCI (Van de Schoot et al., 2020).
This program uses text mining and active learning to build a customizable machine learning model for article inclusion.
We used a naive Bayes model, and focused on exclusion of irrelevant papers.
In ASReview, an additional 541 papers were screened.
Screening again focused on articles most likely to be excluded, and continued until, among the most recently screened 100 papers, only 6 were excluded.
The screening procedure is detailed in Figure \ref{prismachart}.
In total, 6305 papers were retained for analysis.

\begin{figure}
\includegraphics[width=6.5in]{prismachart} \caption{Record screening flowchart}\label{fig:prismachart}
\end{figure}

@@

The corpus for this first analysis consisted of the author-provided keywords for the selected articles.
We extracted keywords by document, and used a dictionary approach
to classify related terms.
The dictionary was created specifically for this study.
The lead author composed a first draft of the dictionary based on prior knowledge of the field.
This draft was subsequently updated in two ways:
First, while writing the introduction for this paper, key terms from the theoretical and empirical literature were added to the dictionary.
Second, by including commonly occurring uncategorized words during preliminary analyses of the data.
An exclusion list of methodological terms and other non-substantive words was generated using the same procedure.

\hypertarget{structural-topic-modeling}{%
\subsection{Structural topic modeling}\label{structural-topic-modeling}}

To determine whether the corpus could

@@

\leavevmode\hypertarget{ref-Ouzzani2016}{}%
Ouzzani, M., Hammady, H., Fedorowicz, Z., \& Elmagarmid, A. (2016). Rayyana web and mobile app for systematic reviews. \emph{Systematic Reviews}, \emph{5}(1), 210. \url{https://doi.org/10.1186/s13643-016-0384-4}

@@

\leavevmode\hypertarget{ref-van_de_schoot_rens_2020_3828293}{}%
Van de Schoot, R., De Bruin, J., Schram, R., Zahedi, P., De Boer, J., Weijdema, F., \ldots{} Oberski, D. (2020). ASReview: Active learning for systematic reviews (Version v0.9.5). Zenodo.
